### 2016-04-08 EU-Circle/eu-circle_case-study-3.Rmd
Update for Climatrans: precipitation and hot summer days
paper58

```{r}
library(esd)
```

---------------------------------
```{r,eval=FALSE}
## Get MIDAS preciptation data that has laready been retrieved 
## from the MIDAS data base (UK Met Office)
source('readmidas.R')
```

>>>>

```{r,echo=TRUE}  
## Load the necessary R-package
library(esd)
## Information about the system and session
Sys.info()
sessionInfo()
```

---------------------------------
```{r,eval=FALSE}
## Get MIDAS preciptation data that has laready been retrieved 
## from the MIDAS data base (UK Met Office)

```
